Ice sheet mass flows

### 2024-07-24 sankey.tex
Mass gain not at 90 degrees

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/60,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, top color=ice, bottom color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG}, angle=-90,
        at={[xshift=5mm,yshift=-3mm]MG.right}, anchor=right}
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=0mm]MGa.right) {Mass gain: \qq{MGa}};
      \sankeyoutin{MG}{MGa}
    \fi

@@

      \sankeystart[red]{ML}
      \sankeyadvance[red]{ML}{5mm}
      \sankeyoutin[red-to-ice]{ML}{MLi}
    }{ % mass gain
      \sankeyadvance[ice-to-black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[xshift=-15mm,yshift=8mm]RFZi.right}, anchor=left, angle=-45}
    }

>>>>

    \sankeyset{
      %% comment for gray outline
      draw/.style={
        draw=white,
        line width=0pt,line cap=round,line join=round,
      },
      start style=arrow,end style=arrow,
      %% fill/.style={fill=yellow!10,line width=0pt,draw=yellow!10},
      ratio=1mm/60,
      minimum radius=0mm,
      water/.style={fill/.style={draw=water,line width=0pt,fill=water,},},
      ice/.style={fill/.style={draw=ice,line width=0pt,fill=ice,},},
      air/.style={fill/.style={draw=air,line width=0pt,fill=air,},},
      black/.style={fill/.style={draw=black,line width=0pt,fill=black,},},
      red/.style={fill/.style={fill=none, top color=red, bottom color=red},},
      ice-to-water/.style={fill/.style={fill=none, left color=ice, right color=water},},
      ice-to-air/.style={fill/.style={fill=none, left color=ice, right color=air},},
      ice-to-black/.style={fill/.style={fill=none, left color=ice, right color=black},},
      ice-to-air-vert/.style={fill/.style={fill=none, top color=ice, bottom color=air},},
      ice-to-water-vert/.style={fill/.style={fill=none, bottom color=ice, top color=water},},
      water-to-air-vert/.style={fill/.style={fill=none, right color=water, left color=air},},
      water-to-air/.style={fill/.style={fill=none, left color=water, right color=air},},
      air-to-ice/.style={fill/.style={fill=none, left color=air, right color=ice},},
      red-to-ice/.style={fill/.style={fill=none, left color=red, right color=ice},},
      water-to-ice/.style={fill/.style={fill=none, left color=water, right color=ice},},
      black-to-ice/.style={fill/.style={fill=none, bottom color=ice, top color=black},},
      in-black/.style={draw/.style={draw=gray,thick=3},},
      out-red/.style={draw/.style={draw=red,thick=3},},
      debug label/.style={
        overlay,
        draw,
        font=\tiny,
        text=debug color,text opacity=1,
        inner sep=.1em,
        fill=white,fill opacity=0.5,
        rounded corners=.1em,
        %% node contents={\name (\qty)},
        node contents={\name},
      },
    }

@@

    \ifnum \numexpr\Q{vMG} > \Q{vML}
      \sankeynode{name=MGa, quantity=\qq{MG}, angle=-35,
        at={[xshift=5mm,yshift=-3mm]MG.right}, anchor=right}
      \node[font=\tiny, anchor=east]
      at ([yshift=0mm,xshift=0mm]MGa.right) {Mass gain: \qq{MGa}};
      \sankeyoutin[ice-to-black]{MG}{MGa}
    \fi

@@

      \sankeystart[red]{ML}
      \sankeyadvance[red]{ML}{5mm}
      \sankeyoutin[red-to-ice]{ML}{MLi}
    }{ % mass gain
      \sankeyadvance[black]{MGa}{3mm}
      \sankeyend[black]{MGa}
      \sankeynode{name=FGi, quantity=\Q{vFRGAIN},
        at={[xshift=-15mm,yshift=8mm]RFZi.right}, anchor=left, angle=-45}
    }
